Approximate State Abstraction

### 2016-01-21 paper/paper.tex
intro thingy

\documentclass{article}
\usepackage{times}
\usepackage{graphicx}
\usepackage{subfigure} 
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{subfigure}
\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
\usepackage{icml2016/icml2016} 
\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage

@@

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}

@@

% Quick MDP blurb?

% Phi notation

% Evluation of Abstract MDP

% Abstract MDP, Ground MDP, Homogenizing Gun

% Previous state aggregation stuff? Or should be in related work?

>>>>

\documentclass{article}
\usepackage{times}
\usepackage{graphicx}
\usepackage{subfigure} 
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{algorithmic}
\usepackage{subfigure}
\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
\usepackage{icml2016/icml2016} 
\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage

@@

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}
\newcommand\defn[1]{{\bf Definition:} #1}

@@

% Abstract policy using in ground.
In general we are interested in how policies defined over the abstract MDP perform in the ground MDP. To leverage a policy defined in the abstract in the ground, we map a ground state into the abstract state space, and query the abstract policy for behavior. Specifically:
\begin{equation}
\pi_A(s) = \pi_A(\phi(s)),\ s \in \mathcal{S}_G
\end{equation}

We evaluate the value of the abstract policy in the ground MDP by following the abstract policy:
\begin{equation}
V^{\pi_A}(s) = \mathcal{R}_G(s,\pi_A(a)) + \gamma \sum_{s' \in \mathcal{S}_G} \mathcal{T}_G(s,\pi_A(a),s')V^{\pi_A}(s')
\end{equation}

\subsection{Exact Abstraction Framework}

\citep{li2006towards} develop a framework for state abstraction in \acp{MDP}, the notation for which is defined in the previous section. Here we survey their main results that we extend to the framework of approximate abstraction.

In particular, they define the following five classes of state abstractors, inspired by existing methods for state abstraction in \acp{MDP}. For brevity, we include those which we build upon directly (see their paper for full details).

\defn{A $Q^*$-irrelevance abstraction, $\phi_{Q^*}$, is such that:
\begin{equation}
\phi_{Q^*}(s_1) = \phi_{Q^*}(s_2) \longrightarrow \forall a\ \left(Q^*(s_1,a) = Q^*(s_2,a)\right)
\end{equation}
}

\defn{A model-irrelevance abstraction, $\phi_{model}$, is such that:
\begin{multline}
\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \forall a\ \mathcal{R}_G(s_1,a) = \mathcal{R}_G(s_2,a) \\
\end{multline}
And:
\begin{multline}
\phi_{model}(s_1) = \phi_{model}(s_2) \rightarrow \\ \forall a \sum_{s' \in \phi^{-1}(\phi(s_1))} \mathcal{T}_G(s_1,a,s') =\sum_{s' \in \phi^{-1}(\phi(s_2))} \mathcal{T}_G(s_2,a,s') \\
\end{multline}
}
